The \dealii Library, Version 9.7

### 2025-09-01 9.7/paper.tex
small update
clarify sentence

\author[9]{Luca~Heltai}
\affil[9]{Department of Mathematics, University of Pisa,
Via Buonarroti 1/c, 56127 Pisa, Italy.}

@@

\item A common operation in finite element codes is to ask whether
  a specific shape function belongs to a particular solution
  variable. In the past, this was implemented by using the

>>>>

\author[9]{Luca~Heltai}
\affil[9]{Department of Mathematics, University of Pisa,
Via Buonarroti 1/c, 56127 Pisa, Italy. {\texttt{luca.heltai@unipi.it}}}

@@

\item A common operation in codes implementing finite element problems with
  several solution variables is to ask whether
  a specific shape function belongs to a particular
  variable, for example the pressure in a Stokes problem. In the past, this was
  implemented by using the
